Call Center Regression Data Analysis

### 2022-11-30 Manuscript/Manuscript.tex
commit #update
commit #final cleanup

\begin{abstract}
 With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
 in the United States alone, call centers play a pivotal role in a business' success.In this paper, call center volume was forecasted and
 models were created to predict the number of agents needed to meet critical attributes such as waittime, calltime, and holdtime. 
 Forecasting gives businesses the ability to make informed business decision and develop data-driven strategies. In the literature it is very
 common to see call center volume being predicted using different techniques, but there is very limited studies on attempting to correlate
 the number of agents needed. Through Regression techniques, there are 8 models proposed to model the number of agents needed based on waittime,
 calltime, goaltime, and the amount of calls handled.
\end{abstract}

\section*{Introduction}
  With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
that will save a company time, money, and unneccessary obstacles. \citep{feinberg2002operational} claims call centers serve as a source of service recovery, added value, market intelligence, and strategic advantage
In the banking industry, calls can range from inquires, transfers, payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking and are capable of handling customer impatience. \citep{brown2005statistical}

  Many studies have been done working with call center volumes as presented in Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
Here an Autoregressive moving average (ARIMA) model is used, which is depicted in the paper as:
\begin{equation}
  \label{eq:ARIMA Standard}
  \Phi(B)(x_i -\mu)=\theta_q(B)\varepsilon_t
\end{equation}
Ibrahim uses multiple ARIMA models to depict seasonality with a combination of exponential smoothing. Holt-Winters smoothing is also used,
with three equations of:
\begin{equation}
  \label{eq:Holt-Winters}
  M_t=\alpha_0(X_t-S_{t-s}) + (1-\alpha_0)(M_{t-1}+B_{t-1}),
\end{equation}
\begin{equation}
  \label{eq:Holt-Winters2}
  B_t=\alpha_1(M_t-M_{t-1}) +(1-\alpha_1)B_{t-1},
\end{equation}
\begin{equation}
  \label{eq:Holt-Winters3}
  S_t=\alpha_2(X_t-M_t) +(1-\alpha_2)S_{t-s},
\end{equation}
where $B_{t}$ is the slope component, $M_{t}$ is the level component, $S_{t}$ is the seasonal component, and s is the period of seasonality.
ARIMA models are a great model to create as "they allow the  representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however the paper never goes into detail about
how many agents there should be working at a set time.

@@

time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever V > W), or beginning of service (V = W).
In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing seconds
in waittime could allow for a more efficient contact call system.

@@

  \begin{table}[H]
    \resizebox{\textwidth}{!} {
    \begin{tabular}{ l | l |}
      {\bf Dependent Variable} & {\bf R-squared Value}\\
    \hline
    Wait Time& 0.1642 \\
    \hline
    Call Time& 0.0569\\
    \hline
    Goal Met& 0.2458\\
    \hline
    Interaction Value& 0.234\\
    \end{tabular}
    }
    \end{table}
R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
Overall, the higher the R-squared the better.
\section*{Discussion}
Overall, the best agent model would be the model with the highest R-squared value and Pearson Coefficient. In this case, this would be
AvgGoalMet= 0.986 - 0.216*CallsPerAgent. A close second place would be AvgWaittime= -5.292 + 61.148*CallsPerAgent, as it had a decent 
Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
r-squared value. Overall the other 3 models are would suggest to an individual to use to determine how many agents
there business to have. Unfortunately, there are so many aspects to just this. In regards to a business perspective, the call center must have
a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance in between to ultimately maximize efficiency.
We were also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
a week.

@@

Another challenge was dealing with the time complexities in the dataset. There are 6 days of the week, 47 15-minute-intervals across any day, which each occur a different number of times,
and 213 15-minute-intervals across each week. This does not average out between days of the week. There was also 139 weeks in the data, 971 days in all the data, and
27377 15-minute-intervals in all the data. So this fails to account for discrepancies in between days of the week. Also, Call time and any values
about the all are data explicitly about the call so they are in the row in the itself, so we have to normalize the number of agents by number of calls During
that period recorded before we run a model comparing both values. So overall, there was a lot of data cleaning and preparing needed in this dataset, that
took time away from the data analysis.

  I still believe this study can be expanded on. Monday has a wait time of 175 seconds while Friday has a wait time of 88.2 seconds. Possibly multivariate regression technqiues could be used to model the number of agents needed.
With the data at my hands, I could also try to answer questions such as if call length is dependenton call reason or even do an analysis on if all agents are performing
on the same level. In detail, \citep{evensen1999effective} believes that "Since the primary interface between a financial institution and its customer is a service
representative, this element strongly influences an institution's ability to deliver quality service.An organization’s human resource (HR) practices effect how well its employees are able to perform. More
specifically, human resource practices directly influence how knowledgeable an employee is about the product offering, whether or not an employee is empowered to resolve customer issues in real time, and the
level of turnover within the organization". This is an interesting point as one could analyze how Human Resources Data plays a role in qualities like AgentHandleTime that reflects on the agents performance. Another interesting question to look into was the abandonment 
rate and if how many times someone will call back the same day. I personally did not look into the chat feature that much, but I am sure that there is some interesting information like if people tend to reuse often.
Another topic of interest is how does call center volume change on when there is an information technology problem such as the online banking services having an outage?

>>>>

\begin{abstract}
 With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
 in the United States alone, call centers play a pivotal role in a business' success.In this paper, call center volume was forecasted and
 models were created to predict the number of agents needed to meet critical attributes such as waittime, calltime, and holdtime. 
 Forecasting gives businesses the ability to make informed business decision and develop data-driven strategies. In the literature it is very
 common to see call center volume being predicted using different techniques, but there is very limited studies on attempting to correlate
 the number of agents needed. Through Regression techniques, there are 4 models proposed to model the number of agents needed based on waittime,
 calltime, goaltime, and the amount of calls handled.
\end{abstract}

\section*{Introduction}
  With over 15 million people employed, a predicted compound annual growth rate (CAGR) of 5.6 percent between 2020 and 2027, and with over 28,000 locations
in the United States alone, call centers play a pivotal role in a business' success. Call centers are a key part of customer service
that saves a company time, money, and unneccessary obstacles. \citep{feinberg2002operational} claims call centers serve as a source of service recovery, added value, market intelligence, and a strategic advantage.
In the banking industry, calls can range from inquires, transfers, payments, reporting, to processing. This means members could call about their account balance, credit card bills, loan applications, 
or unauthorized transactions. It is crucial that a bank is prepared for spikes in calls and have agents knowledgeable in all aspects of banking and are capable of handling customer impatience. \citep{brown2005statistical}

  Many studies have been done working with call center volumes as presented in Modeling and Forecasting Call Center Arrivals \citep{ibrahim2016modeling}.
Here an Autoregressive moving average (ARIMA) model is used, which is depicted in the paper as:
\begin{equation}
  \label{eq:ARIMA Standard}
  \Phi(B)(x_i -\mu)=\theta_q(B)\varepsilon_t
\end{equation}
Ibrahim uses multiple ARIMA models to depict seasonality with a combination of exponential smoothing. Holt-Winters smoothing is also used,
with three equations of:
\begin{equation}
  \label{eq:Holt-Winters}
  M_t=\alpha_0(X_t-S_{t-s}) + (1-\alpha_0)(M_{t-1}+B_{t-1}),
\end{equation}
\begin{equation}
  \label{eq:Holt-Winters2}
  B_t=\alpha_1(M_t-M_{t-1}) +(1-\alpha_1)B_{t-1},
\end{equation}
\begin{equation}
  \label{eq:Holt-Winters3}
  S_t=\alpha_2(X_t-M_t) +(1-\alpha_2)S_{t-s},
\end{equation}
where $B_{t}$ is the slope component, $M_{t}$ is the level component, $S_{t}$ is the seasonal component, and s is the period of seasonality.
ARIMA models are a great model to create as "they allow for the representation of a  wide array of potentially useful predictor functions in  models  which contain relatively few parameters" \citep{newbold1983arima}.
With the combination of Holt-Winters smoothing, Ibrahim creates a great model for forecasting call volume, however the paper never goes into detail about
how many agents that should be working at a set time.

@@

time he must wait before beginning service is his virtual queue time, V. The actual wait time is W = min(A,V), terminated by either abandonment (whenever $V  >  W$), or beginning of service (V = W).
In heavy traffic, even a small fraction of calls that abandon the queue can have a dramatic effect on system performance" \citep{avramidis2005modeling}. This means that just reducing a couple seconds
in wait time could allow for a more efficient contact call system.

@@

  \begin{table}[H]
    \resizebox{\textwidth}{!} {
    \begin{tabular}{ l | l |}
      {\bf Dependent Variable} & {\bf R-squared Value}\\
    \hline
    Wait Time& 0.1642 \\
    \hline
    Call Time& 0.0569\\
    \hline
    Goal Met& 0.2458\\
    \hline
    Interaction Value& 0.234\\
    \end{tabular}
    }
    \end{table}
R-squared values range from 0 to 1. A R-squared value of 1 means that all movements of a variable are completely explained by another variable. 
Overall, the higher the R-squared the better. The model with Goal Met as the dependent variable has the highest R-square value of 0.2458, followed by
the model with Interaction value with an R-squared value of 0.234, then Wait time with a R-squared value of 0.1642, and lastly Call time with a R-squared value of 0.0569.
\section*{Discussion}
Overall, the best agent model would be the model with the highest R-squared value and Pearson Coefficient. In this case, this would be
AvgGoalMet= 0.986 - 0.216*CallsPerAgent. A close second place would be AvgWaittime= -5.292 + 61.148*CallsPerAgent, as it had a decent 
Pearson coefficient and R-squared value. Unfortunately, because of the Pearsons Coefficient I would not recommend the Interaction Value model however even though it had a good 
r-squared value. Overall the other 3 models have a better Pearsons Coefficient and are more useful to an individual to use to determine how many agents
their business to have. Unfortunately, there are so many aspects to staffing a call center. In regards to a business perspective, the call center must have
a budget so it is a difficult road to navigate. But, I believe it is possible to find a balance between budgeting and acheiveing maximize efficiency.
I was also able to forecast call center volume using historical data and the ratio of how many hours the call center is open compared to each day to
a week which is important for managers to know when they designate breaks to their employees.

@@

Another challenge was dealing with the time complexities in the dataset. There are 6 days of the week, 47 15-minute-intervals across any day, which each occur a different number of times,
and 213 15-minute-intervals across each week. This does not average out between days of the week. There was also 139 weeks in the data, 971 days in all the data, and
27377 15-minute-intervals in all the data. So this fails to account for discrepancies in between days of the week. Also, Call time and any values
about the all are data explicitly about the call so they are in the row in the itself, so we have to normalize the number of agents by number of calls during
that period recorded before I ran a model comparing both values. So overall, there was a lot of data cleaning and preparing needed in this dataset, that
took time away from the data analysis.

  I still believe this study can be expanded on. Monday has a wait time of 175 seconds while Friday has a wait time of 88.2 seconds. Possibly multivariate regression technqiues could be used to model the number of agents needed.
With the data at my hands, I could also try to answer questions such as if call length is dependenton call reason or even do an analysis on if all agents are performing
on the same level. In detail, \citep{evensen1999effective} believes that "Since the primary interface between a financial institution and its customer is a service
representative, this element strongly influences an institution's ability to deliver quality service. An organization’s human resource (HR) practices effect how well its employees are able to perform. More
specifically, human resources practices directly influence how knowledgeable an employee is about the product offering, whether or not an employee is empowered to resolve customer issues in real time, and the
level of turnover within the organization". This is an interesting point as one could analyze how Human Resources Data plays a role in qualities like AgentHandleTime that reflects on the agents performance. Another interesting question to look into was the abandonment 
rate and if how many times someone will call back the same day. I personally did not look into the chat feature that much, but I am sure that there is some interesting information like if people tend to reuse often.
Another topic of interest is how does call center volume change on when there is an information technology problem such as the online banking services having an outage?
